Temporal magick or logic

### 2015-12-02 inteligentagents/notes.tex
added proof deleted inbetween doc statementst s
added notes from the lecture and the practicum.

@@

\documentclass{article}
\begin{document}
\author{Jappie Klooster}
\title{Cohen \& Levesque}
\maketitle
\section{Langauge}
DONE = just done
; = sequence
? = test if its true (groovy truth)
+ = is a non detrmenistic choice, collect them in an autcome set.
* = is done a finite but arbitrary number of times, including 0

@@

\section{Rao Georgeff}
\subsection{Time logics}
Brancing vs linear, points vs intervals,
discrete (real numbers) vs continues (complex number)
We'll only look into the future.
\end{document}

\documentclass{article}
\begin{document}
\author{Jappie Klooster}
\title{Temporal magick or logic}
\maketitle
\section{Linear temporal magick}

@@

\end{document}
\documentclass{article}
\begin{document}
\author{Jappie Klooster}
\title{KARO logic}
\maketitle

@@

You can only uncommit commited actions.
\end{document}

>>>>

\documentclass{article}
\begin{document}
\author{Jappie Klooster}
\title{Temporal magick or logic}
\maketitle

@@

\section{Langauge}
DONE = just done
; = sequence
? = test if its true (groovy truth)
+ = is a non detrmenistic choice, collect them in an autcome set.
* = is done a finite but arbitrary number of times, including 0

@@

\section{Rao Georgeff}
\subsection{Time logics}
Brancing vs linear, points vs intervals,
discrete (real numbers) vs continues (complex number)
We'll only look into the future.
\section{Linear temporal magick}

@@

@@

You can only uncommit commited actions.

\section{practical}
\begin{prooftree}
	\AxiomC{$\vDash \Diamond (p\vee q)\wedge \Box \neg q)\to \Diamond p$}
	\UnaryInfC{To proof $m,\sigma \vDash \Diamond (p\vee q)\wedge \Box \neg q)\to \Diamond p$}
	\UnaryInfC{To proof $m,\sigma \vDash \Diamond (p\vee q)\wedge \Box \neg q)\Rightarrow m,\sigma \vDash \Diamond p$}
	\UnaryInfC{To proof $m,\sigma \vDash \Diamond (p\vee q)$ and $\Box \neg q)\Rightarrow m,\sigma \vDash \Diamond p$}
	\UnaryInfC{To proof exists $m,\sigma^n \vDash p$ or $m,\sigma^n \vDash q$
	and for all $m,\sigma^m \vDash \neg q$ then exists $m,\sigma^k \vDash p$}
\end{prooftree}

\begin{prooftree}
	\AxiomC{$\vDash A \phi \to \phi$}
	\UnariyInfC{To prove: for all $M,v,w_t \vDash A \phi \to \phi$}
	\UnariyInfC{Take arbitrary $M,v,w_t$ to prove: for all $M,v,w_t \vDash A \phi \to \vDash \phi$}
	\UnariyInfC{To prove: for all $M,v,w_t \vDash A \phi \Rightarrow m,\sigma \vDashM,v,w_t \vDashM,v,w_tM,v,w_t \vDash \phi$}
	\UnariyInfC{Assume $M,v,w_t \vDash A \phi$ ie  
	$M,v,w_1, w_2, \ldots \vDash \phi$ for all 
	$w_1, w_2, \cdots$ with $t_1 =t$
	}
\end{prooftree}
\begin{prooftree}
\end{prooftree}
	\AxiomC{$\neg\vDash A\Diamond \phi \to E\Box \phi$}

\section{Persistance problem}
Closed world assumption = In databases, everything that is not in the
database is not true.

If I describe an action I want a minimal description of what change
and what does not.

\section{Situational calculus Macarty}
calculus framework, not a logic proper.

$Result(A,s)$ or do. Normally its written like $s\vDash p$

\subsection{Sidenote}
There is a big difference between european AI and american.
American AI is much more applied. And McCarthy is more like a `god'.
In europe modal logic is much more used.

\subsection{Calculus}
\subsubsection{Herbrand situation}
A situation is always a sequance of actions performed on the initial situation

positive effects starts to hold after the action, and negative it doesn't.

Also describe the things that don't change. These are the 'axioms'.

\subsubsection{The frame problem}
You need a pair of axioms is needed for every fluent and action. This will
result in way to many axioms.

This is solved with default reasoning. Altough writer gave it up eventually.
You need to do a consisty check, this is in modal logic already NP-hard.

\section{Planning}
GPS = General planning system
this has to do with program syntesis

STRIPS, depth first.

\subsection{The susman anomaly}
This can go into a loop, because focusing on one of these goals can
make the other one false.

\subsection{start backwards}
Breadtfirst is then more feasible because there are fewer brances.
\[[\alpha] = wp(\alpha,\gamma)\]

\section{practical X}
i.e = $\RightLeftarrow$
\subsection{9A}
\begin{prooftree}
	\AxiomC{To prove $(m,s)$ $\vDash [\alpha_1;\alpha_2]\phi\LeftRightarrow
[\alpha_1][\alpha_2]\phi$ for all $m,s$}

\UnaryInfC{Suppose $(m,s)$ $\vDash [\alpha_1;\alpha_2]\phi$}
\UnaryInfC{ie for all s': $R_{\alpha_1;\alpha_2}(s,s')\Rightarrow m,s$}
\UnaryInfC{ie for all s': $(\exists t: R_{\alpha_1}(s,t)$ and
$R_{\alpha_2}(t,s') \Rightarrow m,s' \vDash\phi$}
\UnaryInfC{ie for all s': $\forall t[ : R_{\alpha_1}(s,t)$ and
$R_{\alpha_2}(t,s') \Rightarrow m,s' \vDash\phi]$}

\UnaryInfC{$\forall s': \forall t[ : R_{\alpha_1}(s,t)$ and
$R_{\alpha_2}(t,s') \Rightarrow m,s' \vDash\phi]$}
\UnaryInfC{$\forall t: \forall s[ : R_{\alpha_1}(s,t)$ and
$R_{\alpha_2}(t,s') \Rightarrow m,s' \vDash\phi]$}

\UnaryInfC{$\forall t: R_{\alpha_1}(s,t) \Rightarrow [\forall S'
R_{\alpha_2}(t,s') \Rightarrow m,s' \vDash\phi]$}

\UnaryInfC{$\forall t: R_{\alpha_1}(s,t) \Rightarrow m,t\vDash[\alpha_2]
\vDash\phi]$}
\UnaryInfC{m,s$\vDash[\alpha_1][\alpha_2]\phi$}
\end{prooftree}

\begin{prooftree}
	\AxiomC{To prove $m,s\vDash <\alpha>(\phi\wedge
	\varphi)\LeftRightarrow(<\alpha>\phi\wedge<\alpha>\varphi)$, for all m,s}
	\UnaryInfC{$m,s\vDash<\alpha>(\phi\wedge\varphi)\LeftRightarrow$}
	\UnaryInfC{$\exists: R_\alpha(s,t)&m,t\vDash\phi\wedge\varphi\LeftRightarrow$}
\end{prooftree}
\begin{prooftree}
	\AxiomC{To proof: $m,s \vDash A\alpha;\alpha_2\LeftRightarrow 
		(A_{\alpha_1}\wedge[\alpha_1]A_{\alpha_2})$}
	\UnaryInfC{Assume arb. $m,s \vDash A\alpha_1;\alpha_2\LeftRightarrow$}
	\UnaryInfC{$\alpha_1;\alpha_2 \exists C (m,s) \LeftRightarrow$}
	\UnaryInfC{$\alpha_1 \exists C (m,s) \& \alpha_2 \exists C (m,s)\LeftRightarrow$}
	\UnaryInfC{$m,s \vDash A\alpha_1 \exists C (m,s) \& R_{\alpha_1}(mcs)
	\vDash A\alpha_2 \LeftRightarrow$}
	\UnaryInfC{$m,s \vDash A\alpha_1 \& \forall(m',s'):R_\alpha_1
	(m,s)(m',s')\rightarrow m',s')\vDash A\alpha_2 \LeftRightarrow$}
	\UnaryInfC{$m,s \vDash A\alpha_1 \& m,s\vDash [\alpha_1]A\alpha_2 \LeftRightarrow$}
	\UnaryInfC{$m,s \vDash A\alpha_1 \& \wedge [\alpha_1]A\alpha_2 \LeftRightarrow$}
\end{prooftree}
\end{document}
